A Fast Unified Model for Parsing and Sentence Understanding

### 2016-06-06 writing/hard_stack_paper/paper.tex
CP's changes

\author{
Samuel R.\ Bowman$^{1,2,3,}$\thanks{~\,The first two authors contributed equally.} \\
\texttt{\small sbowman@stanford.edu} \\
\And
Jon Gauthier$^{2,3,4,*}$ \\
\texttt{\small jgauthie@stanford.edu} \\
\And
Abhinav Rastogi$^{3,5}$ \\
\texttt{\small arastogi@stanford.edu} \\
\AND
Raghav Gupta$^{2,3,6}$ \\
\texttt{\small rgupta93@stanford.edu} \\
\And
Christopher D.\ Manning$^{1,2,3,6}$\\
\texttt{\small manning@stanford.edu}\\
\And
Christopher Potts$^{1}$\\
\texttt{\small cgpotts@stanford.edu}
\AND\\[-3ex]
{$^{1}$Stanford Linguistics\quad
$^{2}$Stanford NLP Group\quad
$^{3}$Stanford AI Lab}\\
{$^{4}$Stanford Symbolic Systems\quad
$^{5}$Stanford Electrical Engineering\quad
$^{6}$Stanford Computer Science}
}

@@

We evaluate SPINN on the task of natural language inference \citep[NLI, a.k.a.\ recognizing textual entailment, or RTE;][]{dagan2006pascal}. NLI is a sentence pair classification task, in which a model reads two sentences (a premise and a hypothesis), and outputs a judgment of {\it entailment}, {\it contradiction}, or {\it neutral}, reflecting the relationship between the meanings of the two sentences. Below is an example sentence pair and judgement from the SNLI corpus which we use in our experiments:

@@

\begin{table*}[t]\small
\begin{center}
\begin{tabular}{lrlrrrr}
\toprule
Param.     & Range & Strategy        & RNN       & SPINN-PI-NT   & SPINN-PI  & SPINN \\
\midrule 
Initial LR & 2e-4--2e-2 & \textsc{log} & 5e-3  & 3e-4 & 7e-3  & 2e-3\\
L2 regularization $\lambda$ & 8e-7--3e-5   & \textsc{log} & 4e-6  & 3e-6   & 2e-5  & 3e-5\\
Transition cost $\alpha$  & 0.5--4.0 & \textsc{lin} & --- & --- & ---  & 3.9    \\
Embedding transformation dropout keep rate & 80--95\% & \textsc{lin} & --- & 83\% & 92\%  & 86\%\\
Classifier MLP dropout keep rate & 80--95\% & \textsc{lin} & 94\%  & 94\%   & 93\%  & 94\%\\
Tracking LSTM size $D_\text{tracking}$ & 24--128 & \textsc{log} & --- & --- & 61  & 79\\
Classifier MLP layers & 1--3 & \textsc{lin} & 2 & 2 & 2 & 1\\
\bottomrule
\end{tabular}
\end{center}
\caption{
\label{tab:hyperparams}
Hyperparameter ranges and values. \ii{Range} shows the hyperparameter ranges explored during random search. \ii{Strategy} indicates whether sampling from the range was uniform, or log--uniform.
}
\end{table*}

@@

\begin{table*}[t]
  \centering\small
  \begin{tabular}{lrrrr}
    \toprule
Model                   & Params.    & Trans. acc. (\%)  &   Train acc. (\%)  &   Test acc. (\%) \\
\midrule
\multicolumn{5}{c}{\textbf{Previous non-NN results}}\\
Lexicalized classifier \citep{snli:emnlp2015}
                        & ---                & ---                    &   99.7   &   78.2      \\
\midrule
\multicolumn{5}{c}{\textbf{Previous sentence encoder-based NN results}}\\
100D LSTM encoders \citep{snli:emnlp2015}
                        & 221k               & ---               &   84.8   &   77.6      \\
1024D pretrained GRU encoders \citep{DBLP:journals/corr/VendrovKFU15}
                        & 15m                & ---              &   98.8   &   81.4       \\
300D Tree-based CNN encoders \citep{mou2015recognizing}
                        & 3.5m                & ---             &   83.4   &   82.1       \\
\midrule
\multicolumn{5}{c}{\textbf{Our results}}\\
300D LSTM RNN encoders         & 3.0m                  & ---                &   83.9      &   80.6       \\
300D SPINN-PI-NT (\ii{parsed input, no tracking}) encoders
                        & 3.4m                  & ---                &   84.4      &   80.9       \\
300D SPINN-PI (\ii{parsed input}) encoders
                        & 3.7m                  & ---                &   89.2      &   \textbf{83.2}       \\
300D SPINN (unparsed input) encoders
                        & 2.7m                  & 92.4           &   87.2    &   82.6      \\
% \result{300D SPINN-PI, sequence-based attn.   }
%                         & ?                  & --                &   ?      &   86.3dv         \\
% \result{300D SPINN-PI, tree-based attn. }
%                         & ?                  & --                &   ?      &   \textbf{?}\\
% \midrule
% \multicolumn{5}{c}{Other previous NN results}\\
% \midrule
% 100D LSTM w/ word-by-word attention \citep{rocktaschel2015reasoning}
%                         & 252k               & --              &   85.3   &   83.5       \\
% 300D mLSTM word-by-word attention model \citep{DBLP:journals/corr/WangJ15b}
%                         & 1.9m               & --             &   92.0   &   86.1      \\
% 300D LSTMN with deep attention fusion \citep{cheng2016long}
%                         & 1.4m               & --                &   92.3   &   \textbf{89.1}      \\
    \bottomrule
  \end{tabular}
\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. Params. is the approximate number of trained parameters (excluding word embeddings for all models). Trans. acc. is the model's accuracy in predicting parsing transitions at test time. Train and test are SNLI classification accuracy.}
\end{table*}

@@

Because this paper aims to introduce a general purpose model for sentence encoding, we do not pursue the use of soft attention \citep{bahdanau2014neural,rocktaschel2015reasoning}, despite its demonstrated effectiveness on the SNLI task.\footnote{Attention based models like \citet{rocktaschel2015reasoning,wang2015learning} and the unpublished \citet{cheng2016long} have shown accuracies as high as 86.1\% on SNLI, but are more narrowly engineered to suit the task, and do not yield sentence encodings.} However, we expect that it should be possible to productively combine our model with soft attention to reach state-of-the-art performance.

>>>>

\author{
Samuel R.\ Bowman$^{1,2,3,}$\thanks{~\,The first two authors contributed equally.} \\
\texttt{\small sbowman@stanford.edu} \\
\And
Jon Gauthier$^{2,3,4,*}$ \\
\texttt{\small jgauthie@stanford.edu} \\
\And
Abhinav Rastogi$^{3,5}$ \\
\texttt{\small arastogi@stanford.edu} \\
\AND
Raghav Gupta$^{2,3,6}$ \\
\texttt{\small rgupta93@stanford.edu} \\
\And
Christopher D.\ Manning$^{1,2,3,6}$\\
\texttt{\small manning@stanford.edu}\\
\And
Christopher Potts$^{1,6}$\\
\texttt{\small cgpotts@stanford.edu}
\AND\\[-3ex]
{$^{1}$Stanford Linguistics\quad
$^{2}$Stanford NLP Group\quad
$^{3}$Stanford AI Lab}\\
{$^{4}$Stanford Symbolic Systems\quad
$^{5}$Stanford Electrical Engineering\quad
$^{6}$Stanford Computer Science}
}

@@

We evaluate SPINN on the task of natural language inference \citep[NLI, a.k.a.\ recognizing textual entailment, or RTE;][]{dagan2006pascal}. NLI is a sentence pair classification task, in which a model reads two sentences (a premise and a hypothesis), and outputs a judgment of {\it entailment}, {\it contradiction}, or {\it neutral}, reflecting the relationship between the meanings of the two sentences. Below is an example sentence pair and judgment from the SNLI corpus which we use in our experiments:

@@

\begin{table*}[t]\small
\begin{center}
\begin{tabular}{lrlrrrr}
\toprule
Param.     & Range & Strategy        & RNN       & SPINN-PI-NT   & SPINN-PI  & SPINN \\
\midrule 
Initial LR & 2e-4--2e-2 & \textsc{log} & 5e-3  & 3e-4 & 7e-3  & 2e-3\\
L2 regularization $\lambda$ & 8e-7--3e-5   & \textsc{log} & 4e-6  & 3e-6   & 2e-5  & 3e-5\\
Transition cost $\alpha$  & 0.5--4.0 & \textsc{lin} & --- & --- & ---  & 3.9    \\
Embedding transformation dropout keep rate & 80--95\% & \textsc{lin} & --- & 83\% & 92\%  & 86\%\\
Classifier MLP dropout keep rate & 80--95\% & \textsc{lin} & 94\%  & 94\%   & 93\%  & 94\%\\
Tracking LSTM size $D_\text{tracking}$ & 24--128 & \textsc{log} & --- & --- & 61  & 79\\
Classifier MLP layers & 1--3 & \textsc{lin} & 2 & 2 & 2 & 1\\
\bottomrule
\end{tabular}
\end{center}
\caption{
\label{tab:hyperparams}
Hyperparameter ranges and values. \ii{Range} shows the hyperparameter ranges explored during random search. \ii{Strategy} indicates whether sampling from the range was uniform, or log-uniform.
}
\end{table*}

@@

\begin{table*}[t]
  \centering\small
  \begin{tabular}{lrrrr}
    \toprule
Model                   & Params.    & Trans. acc. (\%)  &   Train acc. (\%)  &   Test acc. (\%) \\
\midrule
\multicolumn{5}{c}{\textbf{Previous non-NN results}}\\
Lexicalized classifier \citep{snli:emnlp2015}
                        & ---                & ---                    &   99.7   &   78.2      \\
\midrule
\multicolumn{5}{c}{\textbf{Previous sentence encoder-based NN results}}\\
100D LSTM encoders \citep{snli:emnlp2015}
                        & 221k               & ---               &   84.8   &   77.6      \\
1024D pretrained GRU encoders \citep{DBLP:journals/corr/VendrovKFU15}
                        & 15m                & ---              &   98.8   &   81.4       \\
300D Tree-based CNN encoders \citep{mou2015recognizing}
                        & 3.5m                & ---             &   83.4   &   82.1       \\
\midrule
\multicolumn{5}{c}{\textbf{Our results}}\\
300D LSTM RNN encoders         & 3.0m                  & ---                &   83.9      &   80.6       \\
300D SPINN-PI-NT (\ii{parsed input, no tracking}) encoders
                        & 3.4m                  & ---                &   84.4      &   80.9       \\
300D SPINN-PI (\ii{parsed input}) encoders
                        & 3.7m                  & ---                &   89.2      &   \textbf{83.2}       \\
300D SPINN (unparsed input) encoders
                        & 2.7m                  & 92.4           &   87.2    &   82.6      \\
% \result{300D SPINN-PI, sequence-based attn.   }
%                         & ?                  & --                &   ?      &   86.3dv         \\
% \result{300D SPINN-PI, tree-based attn. }
%                         & ?                  & --                &   ?      &   \textbf{?}\\
% \midrule
% \multicolumn{5}{c}{Other previous NN results}\\
% \midrule
% 100D LSTM w/ word-by-word attention \citep{rocktaschel2015reasoning}
%                         & 252k               & --              &   85.3   &   83.5       \\
% 300D mLSTM word-by-word attention model \citep{DBLP:journals/corr/WangJ15b}
%                         & 1.9m               & --             &   92.0   &   86.1      \\
% 300D LSTMN with deep attention fusion \citep{cheng2016long}
%                         & 1.4m               & --                &   92.3   &   \textbf{89.1}      \\
    \bottomrule
  \end{tabular}
\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. Params.\ is the approximate number of trained parameters (excluding word embeddings for all models). Trans.\ acc.\ is the model's accuracy in predicting parsing transitions at test time. Train and test are SNLI classification accuracy.}
\end{table*}

@@

Because this paper aims to introduce a general purpose model for sentence encoding, we do not pursue the use of soft attention \citep{bahdanau2014neural,rocktaschel2015reasoning}, despite its demonstrated effectiveness on the SNLI task.\footnote{Attention-based models like \citet{rocktaschel2015reasoning,wang2015learning} and the unpublished \citet{cheng2016long} have shown accuracies as high as 86.3\% on SNLI, but are more narrowly engineered to suit the task, and do not yield sentence encodings.} However, we expect that it should be possible to productively combine our model with soft attention to reach state-of-the-art performance.
